Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/intro.tex

Our contribution is threefold:
\begin{itemize} 
\item We show that the Q-function collapses to the V-function in near-continuous time, and thus that
    standard Q-learning is ill-behaved in this setting.
  \item Our analysis of limit properties in near continuous environments leads to a robust off-policy algorithm. In particular,
    it provides insights on how to design architectures, constraints exploration, as well as learning rates scalings.
  \item We empirically show that standard Q-learning methods are not robust to changes in time discretization, and that our algorithm provides huge gain in that domain.
\end{itemize}

>>>>

Our contribution is threefold:
\begin{itemize} 
\item We show that the Q-function collapses to the V-function in near-continuous time, and thus that
    standard Q-learning is ill-behaved in this setting.
  \item Our analysis of limit properties in near continuous environments leads to a robust off-policy algorithm. In particular,
    it provides insights on how to design architectures, constraint exploration, and scale learning rates.
  \item We empirically show that standard Q-learning methods are not robust to changes in time discretization, and that our algorithm provides notable gains in that domain.
\end{itemize}
